\sysfull

### 2017-07-27 paper/evaluation.tex

We compare the performance of \sys against the state-of-the-art intermittent execution approach---Chain~\cite{chain}.

The applications that were used in the evaluation are given in Table~\ref{table:benchmark_list}.

\begin{table}
	\begin{tabular}{|c|c|c|}
		\hline
		Name & SLOC (\sys) & SLOC (Chain~\cite{chain})\\
		\hline\hline
		Temperature sensing & 388 & 721 \\ %53\%
		Cuckoo & 483 & 762 \\ %63\%
		RSA & 887 & 1233 \\ %71\%
		DFT & --- & --- \\ %Two resolutions: 4 and 8 Bytes
		Huffman & --- & --- \\ %Data decompression size: 100 bytes
		Selection sort & --- & --- \\
		\hline
	\end{tabular}
\caption{List of benchmarks used in \sys evaluation.}
\label{table:benchmark_list}
\end{table}

\subsection{Continuous Power Supply}
\label{sec:results_continuous_power}

@@

%Set of experiments

%- Compiler result: taskifying completion time, correctness, 
%- Task coalescing experiment: with WISP at 3 distances and with fixed power, for all apps, compared against chain, show amount of task merged, time to completion/inter-operation time, overhead (in terms of what?), energy consumed
%- Battery-less microphone: with \sys and without \sys, compared against Chain, 
%- Paging/memory experiment: ?

\subsection{Intermittent Power Supply}
\label{sec:intermittent_continuous_power}

>>>>

We are now ready to present experimental results of \sys performance. We start with describing the hardware environment (Section~\ref{sec:results_hardware}) followed by the software environment (Section~\ref{sec:results_software}) and we concluded by the evaluation results (Section~\ref{sec:results_evaluation}).

\subsection{Hardware Suite Description}
\label{sec:results_hardware}

In the experiments we used WISP\,5.1~\cite{wisp5,wisp} (with MSP430FR5969~\cite{wolverine} 64\,kB FRAM) or MSP430XXX launchpad~\cite{} (hardware type will be specified per experiment in Section~\ref{sec:results_evaluation}). WISP\,5.1 has been programmed using TI FET for experiments. FET was also used as a power supply in non-intermittent power experiment. To measure energy consumption of the applications (refer to Section~\ref{sec:results_software}) EDB~\cite{edb} was used. In experiments involving wireless power, WISP was powered through RFID reader (Impinj R1000 with firmware version 3.2.4.240~\cite{r1000_data_sheet}) connected to Liard RFMAX S9028PCRJ 8\,dBic~\cite{atlas2015}. RFID reader is controlled by a PC running Ubuntu 10.4 executing open source Python-based \emph{sllurp} library~\cite{sllrp_github} enabling low-level RFID reader control. Transmitted power of the RFID reader was 30\,dBm at 915\,MHz center frequency. For distance controlled experiments, WISP was positioned at hollow paper tubes placed directly on a lying antenna.

\subsection{Software Suite Description}
\label{sec:results_software}

We compare \sys against state of the art intermittent execution approach---Chain~\cite{chain}. We need to note that although another very relevant task-based runtime has been recently presented and referenced many times throughout this paper---Alpaca~\cite{alpaca}---we did not have the access to its code during the preparation of this manuscript.

The applications that were used in the evaluation are given in Table~\ref{table:benchmark_list}. These benchmarks are the same ones as used in~\cite{chain,alpaca}.

\begin{table}
	\begin{tabular}{|c|c|c|}
		\hline
		Name & SLOC (\sys) & SLOC (Chain~\cite{chain})\\
		\hline\hline
		Temperature sensing & 388 & 721 \\ %53\%
		Cuckoo & 483 & 762 \\ %63\%
		RSA & 887 & 1233 \\ %71\%
		DFT & --- & --- \\ %Two resolutions: 4 and 8 Bytes
		Huffman & --- & --- \\ %Data decompression size: 100 bytes
		Selection sort & --- & --- \\
		\hline
	\end{tabular}
\caption{List of benchmark programs used in \sys evaluation; SLOC: source lines of code.}
\label{table:benchmark_list}
\end{table}

\subsection{Evaluation}
\label{sec:results_evaluation}

\subsubsection{Compiler Performance}
\label{sec:results_compiler}

Compiler experiment: taskifying completion time of a code run, correctness (manual inspection---proof by example), comparison manual/automatic taskification - fixed power supply

\todo{Provide structure to this section}{Kiwan}

\subsubsection{}
\label{sec:}

@@

Task coalescing experiment: with WISP at 3 distances and with fixed power, for all apps, compared against chain, show amount of task merged, time to completion, overhead (in terms of what?), energy consumed with fixed power

\subsubsection{Memory Management}
\label{sec:results_memory_management}

Paging/memory experiment: page swapping cost (execution time)---comparing against chain and full double buffering approach, show number of page swaps,

\todo{Provide argument for page swapping using hardware support}{Brandon}

\subsubsection{Case Study}
\label{sec:case_study}

Battery-less microphone: with \sys and without \sys, compared against Chain.
